---
title: "Exercises"
author: ''
date: ''
output:
  pdf_document: default
  html_document: default
subtitle: Week 1
---

```{r libraries}
library(ggplot2)
library(dplyr)
library(reshape2)
```


## Exercise 1: Matrices


1. Create a matrix. The matrix should have 10 elements and 2 columns. All the elements of your matrix should be integers. Do not forget to give a name to your matrix.

```{r}
# Put your code in here
mat <- matrix(0:9, ncol = 2) 
```

2. Create another matrix. The matrix should have 10 elements and 5 columns. All the elements of your matrix should be integers. Do not forget to give a name to your matrix.

```{r}
# Put your code in here
mat2 <- matrix(0:9, ncol = 5)
```

3. Multiply the two matrix together. Remember to use the right operator for matrix multiplication. Display the result.

```{r}
# Put your code in here
mat %*% mat2

mat2 %*% mat

try(mat * mat2)
```

What happens if you use the standard multiplication operator?

4. Now create two square matrices and multiply them using the matrix multiplication operator and the normal operator. What do you notice?

```{r}
# Put your code in here
mat <- matrix(1:4, ncol = 2)

mat2 <- matrix(1:4, ncol = 2)

mat %*% mat2

mat * mat2
```


## Exercise 2: Systems of equations


1. Solve the following system

$$
\begin{cases} 5x - 2y + 3z - \alpha = 2  \\ 
x + 4y - z + \alpha = 19\\ 
4x + \frac{1}{2}y + 12z - 6 \alpha = -11\\
2x - y + z - 3 \alpha = -12
\end{cases}
$$

```{r}
# Put your code in here
a <- matrix(c(5, -2, 3, -1, 1, 4, -1, 1, 4, 0.5, 12, -6, 2, -1, 1, -3), nrow = 4, byrow = TRUE)

b <- c(2, 19, -11, -12)

solve(a, b)
```



1. Solve the following system (bis)

$$
\begin{cases} 5x - 2y + 3z - \alpha = {\bf 17}  \\ 
x + 4y - z + \alpha = 19\\ 
4x {\bf -} \frac{1}{2}y + 12z - 6 \alpha = -11\\
2x - y + z - 3 \alpha = -12
\end{cases}
$$

```{r}
# Put your code in here
a <- matrix(c(5, -2, 3, -1, 1, 4, -1, 1, 4, -0.5, 12, -6, 2, -1, 1, -3), nrow = 4, byrow = TRUE)

b <- c(17, 19, -11, -12)

solve(a, b)
```

Exercise 3: derivatives

1. What are the derivatives of the following functions:
  + $f(x) = cos(x)$
  + $f(x) = x + y^2$ for $x$ and for $y$
  + $f(x) = 5x + x^2 - e^x$

```{r}
# Put your code in here
D(expression(cos(x)), "x")
D(expression(x + y^2), c("x"))
D(expression(x + y^2), c("y"))
D(expression(5 * x + x^2 - exp(x)), "x")
```

2. Gradient. Use the `deriv` function to build the gradient of the following functions:
  + $f(x) = cos(x) - sin(x)$
  + $f(x) = 5x + x^2 + 5$
  + $f(x) = x^2 - ln(x) - 3x$
  + $f(x) = x^2 * 5 * y - 2 * y for x and for y$

```{r}


# Put your code in here


d1 <- deriv(expression(cos(x) - sin(x)), "x", function.arg = TRUE)

d1(1:5)

d2 <- deriv(expression(5 * x + x^2 + 5), "x", function.arg = TRUE)

d2(1:5)

d3 <- deriv(expression(x^2 -log(x) - 3 * x), "x", function.arg = TRUE)

d3(1:5)

d4 <- deriv(expression(x^2 * 5 * y - 2 * y), c("x", "y"), function.arg = TRUE)

d4(1:5, 1:5)

```


Exercise 4: Probability

1. If there is 30 balls in an urn what is the probability of drawing any ball?

$1/30$

2. If 10 of those ball are red, what is the probability of drawing a red ball?

$10/30 = 1/3$

3. If the red balls are numbered 1 to 10 and the other balls (let's assume they are black) are numbered 1 to 10 with 2 black balls of each type:
  + what is the probability of the ball drawn being red if it is a 2?
  
  There are 3 balls with the number 2 on them, 2 black and one red so the probability the ball is red if it is a 2 is $1/3$
  
  + What is the probability that the ball is marked with the number 7 if it is black?

  There are 20 black balls and 2 bear the number 7. So the probability that a black ball that is drawn is numbered 7 is $2 / 20 = 1 / 10$.

4. If you throw a fair coin 10 times, what is the probability of getting exactly 4 heads? At least 4 heads?

The probability to get k successes out of 10 trials is: $$\binom{n}{k}p^k(1-p)^{n-k}.$$

So if we replace in this expression, the probability of getting 4 heads is $\binom{10}{4} \frac{1}{2}^4 \frac{1}{2}^{6}$
Which is equal to: `r choose(10, 4) * 0.5^4 * 0.5^6`

For the probability of getting at least for heads, you can think of it as the probability of getting 4 heads plus the probability of getting 5 heads, etc until you reach 10. Or you could think about it as 1 minus the probability of getting 0, 1, 2 or 3 successes.
So it is equal to $1 - \sum_{k = 0}^3{\binom{10}{k} \frac{1}{2}^k \frac{1}{2}^{n-k}}$, that is: `r 1 - (choose(10, 0) * 0.5^0 * 0.5^10 + choose(10, 1) * 0.5^1 * 0.5^9 + choose(10, 2) * 0.5^2 * 0.5^8 + choose(10, 3) * 0.5^3 * 0.5^7)`


5. If you roll a fair 6-sided dice 10 times, what is the probability of getting exactly 3 sixes? What is the probability of getting at least 3 sixes? 

The same logic as in the exercise above applies.
The probability of getting exactly 3 sixes is $\binom{10}{3} \frac{1}{6}^3 \frac{5}{6}^{7}$
Which is equal to: `r choose(10, 3) * (1 / 6)^4 * (5 / 6)^6` 

The probability of getting at least 3 sixes is: $1 - \sum_{k = 0}^2{\binom{10}{k} \frac{1}{6}^k \frac{5}{6}^{10-k}}$, that is: `r 1 - (choose(10, 0) * (1 / 6)^0 * (5 / 6)^10 + choose(10, 1) * (1 / 6)^1 * (5 / 6)^9 + choose(10, 2) * (1 / 6)^2 * (5 / 6)^8)`

Exercise 5: Some games with dice

You and one of your classmates got a number of dice. Now we need to come up with a game using them.

1. First, simulate each of the dice you have. Write a function that when called is going to select 1 of the faces of the dice.

```{r}
# Put your code in here

# In order to simulate a dice you could use the already available
# function called sample()
dice <- sample(1:6, size = 1)
dice
```


2. Now in discussion with one of your classmates, design a simple game were two players successively throw dice. Aim to make it fast, fun and allow for some strategic thinking. Once you have played this game a few times, calculate each players probability of winning. Do the final probabilities seem aligned with your perception when you played the game?


## Exercise 6: Just check that this .Rmd document renders both to pdf and html.

## Exercise 7: The one with the pull request

Fork the [github repository](https://github.com/antoinevernet/BA1820) for the class.

Improve an existing slide in session 1 or session 2, or design a new slide that expand the current slide deck.

Edit the readme to add your name in the contributors section with your cohort name (Business Analytics 1718)

Write a pull request.

If your pull request is accepted (I might require some changes first), you name is now forever in the contributors list.


